Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-11 introduction.tex
Fix wording

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.

>>>>

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound.
